Biogears in Anesthesia Screen Based Simulation

### 2016-02-17 paper_working_on/paper.tex
add experiment intro

@@

\end{document}

>>>>

The reason why physicians don't buy into simulation-based software is due to the fundamental distrust in the models simulation software utilized to generate all the signals and data. And yet, there is no uniformly consented algorithms to describe the complicated nature of human bodies. Thus, the most reliable way to evaluate whether a simulation is fit for real scenario operations is to compare them with the common sense of physicians and doctors. For example, one of the most common thoughts of physicians about the authenticity of scenarios generated by simulation is to see the heart rate of patient when the patient is given different dosage of morphine. If you inject a small dosage of morphine it should somehow make the patient calm down and reduce the heart rate but if you inject more morphine than you should, the drug may be likely to kill a patient.

Inspired by the previous work from this paper \cite{measure_repeatability}

@@

\begin{thebibliography}{1}

  \bibitem{measure_repeatability} Cumin, David, Charlotte Chen, and Alan F. Merry. "Measuring the repeatability of simulated physiology in simulators." Simulation in Healthcare 10.6 (2015): 336-344.

  \bibitem{impj}

  \bibitem{norman}

  \bibitem{fo}

  \end{thebibliography}
\end{document}
